\bf\mftitle

### 2011-03-02 doc/jInfer/paper/paper.tex
more and more

\section*{Related work}
Most of the algorithms named, doesn't have avalaible implementation, nor are made ready to use.
Probably best solution nowadays is \cite{Bex:2008:SSI:1376616.1376750}.
It deals with

\section*{Short architecture overview}

\section*{More work/Open issues}

\section*{Conclusion?}

%\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}
\end{document}

>>>>

\section*{Related work}
Most of the algorithms named, doesn't have avalaible implementation, nor are made ready to use.
Probably best solution nowadays is \cite{Bex:2008:SSI:1376616.1376750}.
It deals with schema infering, user interaction, schema visualization and user-aided refinement.
Authors use their own algorithms for schema inference (\cite{Bex:2006:ICD:1182635.1164139, Bex:2007:IXS:1325851.1325964}).
Compared to our software, they are better in user interaction and schema visualization.
There is no mention of extensibility, however, which we solve as our top priority.

Since both are trying to solve nearly same problem, we predict that we will approach some good ideas from other solution in further work.

Some XML editors also offers XML schema generation, 
% TODO editors - oxygen, stylus, can they do something? how they do it, they are not free

\section*{Short architecture overview}
We divide the process of inference into three steps:
\begin{enumerate}
	\item 
	TODO steps, graph from architecture, short mention of internal structure = grammar
\end{enumerate}	
\section*{Extensibility}
TODO short description of how easily can framework be extended ??? maybe not

\section*{More work/Open issues}
There are still many issues to be worked on.
First is set of supported input/output formats.
On input, one can imagine XML Queries, on output Relax NG or Schematron. 
There is room for implementing schema visualization tool into jInfer, to enable user-aided schema refinement.
Many algorithms published wait to be implemented as jInfer modules, maybe some of them will be tried in study of our master theses.

\section*{Conclusion}
Framework presented aims to be the tool used to obtain schemas from XML/XSD/DTD files (and more inputs after extending).
While maintaining distributable bundle for users, with best of module selections and algorithms implemented so far, we predict it will be used in future studies of new algorithms as a test environment.
Best of them will probably migrate into jInfer source tree to aid common users to solve their document set quickly enough, to even bother with schema generation at all.

Weak side of the solution is the lack of good quality automatic or semi-automatic algorithms to be used by common user.
Goal was to produce stable framework for future development and we hope to negate this issue by implementing master theses in this environment, providing it with bundle of different algorithms, solving different input and output formats and infering more concise schemas.

\nocite{*}
\newpage
\bibliographystyle{alpha}
\bibliography{literature}
\end{document}
